---
title: "Layouts and Faces"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Layouts and Faces}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(scry)
```

The `layout` property categorizes the arrangement of card parts, faces, and
other bounded regions on cards. The layout can be used to programmatically
determine which other properties on a card you can expect.

Specifically:

- Cards with the layouts `split`, `flip`, `transform`, and `double_faced_token`
  will always have a `card_faces` property describing the distinct faces.
- Cards with the layout `meld` will always have a `related_cards` property
  pointing to the other meld parts.

| Layout               | Description                                        | Examples                                                                   |
| -------------------- | -------------------------------------------------- | -------------------------------------------------------------------------- |
| `normal`             | A standard Magic card with one face                | [Example Cards](https://scryfall.com/search?q=layout%3Anormal)             |
| `split`              | A split-faced card                                 | [Example Cards](https://scryfall.com/search?q=layout%3Asplit)              |
| `flip`               | Cards that invert vertically with the flip keyword | [Example Cards](https://scryfall.com/search?q=layout%3Aflip)               |
| `transform`          | Double-sided cards that transform                  | [Example Cards](https://scryfall.com/search?q=layout%3Atransform)          |
| `modal_dfc`          | Double-sided cards that can be played either-side  | [Example Cards](https://scryfall.com/search?q=layout%3Amodal_dfc)          |
| `meld`               | Cards with meld parts printed on the back          | [Example Cards](https://scryfall.com/search?q=layout%3Ameld)               |
| `leveler`            | Cards with Level Up                                | [Example Cards](https://scryfall.com/search?q=layout%3Aleveler)            |
| `class`              | Class-type enchantment cards                       | [Example Cards](https://scryfall.com/search?q=layout%3Aclass)              |
| `saga`               | Saga-type cards                                    | [Example Cards](https://scryfall.com/search?q=layout%3Asaga)               |
| `adventure`          | Cards with an Adventure spell part                 | [Example Cards](https://scryfall.com/search?q=layout%3Aadventure)          |
| `planar`             | Plane and Phenomenon-type cards                    | [Example Cards](https://scryfall.com/search?q=layout%3Aplanar)             |
| `scheme`             | Scheme-type cards                                  | [Example Cards](https://scryfall.com/search?q=layout%3Ascheme)             |
| `vanguard`           | Vanguard-type cards                                | [Example Cards](https://scryfall.com/search?q=layout%3Avanguard)           |
| `token`              | Token cards                                        | [Example Cards](https://scryfall.com/search?q=layout%3Atoken)              |
| `double_faced_token` | Tokens with another token printed on the back      | [Example Cards](https://scryfall.com/search?q=layout%3Adouble_faced_token) |
| `emblem`             | Emblem cards                                       | [Example Cards](https://scryfall.com/search?q=layout%3Aemblem)             |
| `augment`            | Cards with Augment                                 | [Example Cards](https://scryfall.com/search?q=layout%3Aaugment)            |
| `host`               | Host-type cards                                    | [Example Cards](https://scryfall.com/search?q=layout%3Ahost)               |
| `art_series`         | Art Series collectable double-faced cards          | [Example Cards](https://scryfall.com/search?q=layout%3Aart_series)         |
| `reversible_card`    | A Magic card with two sides that are unrelated     | [Example Cards](https://scryfall.com/search?q=layout%3Areversible_card)    |

## Card Faces

Magic cards can include multiple faces on a single piece of card stock. Scryfall
includes information about each of these card faces using the `card_faces`
property on API objects. Please note the following types of multi-face cards and
how Scryfall will describe them:

**Split cards** _(Comp. rules term)_: Split cards are sorceries or instant cards
that include two faces and the caster can choose which face to cast. The back of
a split card is the normal Magic back.

```{r}
scry_card("0f279560-7e9f-4a6d-9fd6-6c8c6bd94a1b")
```

**Flip cards** _(Comp. rules term)_: Flip cards have two parts of a permanent
printed vertically on one side of the card. During play, an ability on the card
causes the permanent to flip (rotate 180°) to the other side. The back of a flip
card is the normal Magic back.

```{r}
scry_card("0b61d772-2d8b-4acf-9dd2-b2e8b03538c8")
```

**Double-faced cards** _(Comp. rules term)_: These cards have two faces on
different sides of the cardstock that are related to each other. The whole card
is a single legal or deckbuilding object. Double-faced cards can either be
transforming or modal.

**Transforming double-faced cards** _(Comp. rules term)_: These cards can either
transform after entering the battlefield, or can be put onto the battlefield
already transformed. Scryfall will use the card_faces object to describe the two
different transformed modes of the card, while the root object will contain data
that applies to both sides. These cards have their layout field set to
"transform".

```{r}
scry_card("b37aa12c-a6b3-4cf8-b5a4-0a999ff12d02")
```

**Modal double-faced cards** _(Comp. rules term)_: Modal DFCs be cast or played
as either half of the card. Scryfall will use the card_faces object to describe
the two different modes of the card, while the root object will contain data
that applies to both sides (such as the color_identity). These cards have their
layout field set to "modal_dfc".

```{r}
scry_card("ba09360a-067e-48a5-bdc5-a19fd066a785")
```

**Reversible cards** _(casual term)_: This term is used by both Scryfall and
WotC to describe a piece of cardstock with two distinct Magic cards or tokens
printed on opposite sides. The two halves of the card are not related to each
other in any way and are treated as two separate objects for gameplay or
deckbuilding. The overall Card object will have its layout field set to
"reversible_card", while the individual card_face objects will have their own
layout fields describing the distinct printings on both sides. Many other fields
for a reversible card move into the card_face objects to describe the distinct
face.

```{r}
scry_card("3e3f0bcd-0796-494d-bf51-94b33c1671e9")
```

**Multi-faced cards** _(casual term)_: This term has no rules meaning and is
used by Scryfall to describe any object with the nested card_faces property.

**Double-sided cards** _(casual term)_: This term has no rules meaning and is
used only casually to refer to any cards with gameplay information on both
sides.
